\textit{Supplementary materials for}: Feature and order manipulations in a free recall task affect memory for current and future lists

### 2023-11-21 paper/supplement.tex
moved most stats to tables
updated abbreviations table, removed page number from first page of supplement, re-ran stats notebook for consistency

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{geometry}
\usepackage{natbib}
\usepackage{pxfonts}
\usepackage{graphicx}
\usepackage{newfloat}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{placeins}
\usepackage{rotating}

@@

\setcounter{equation}{0}
\setcounter{figure}{0}
\setcounter{table}{0}
\setcounter{page}{1}
\setcounter{section}{0}
\makeatletter
\renewcommand{\theequation}{S\arabic{equation}}
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\bibnumfmt}[1]{[S#1]}
\renewcommand{\citenumfont}[1]{S#1}

\maketitle

@@

\caption{\textbf{Recall dynamics in feature-rich free recall (random
conditions).} \textbf{Left panels.} The probabilities of initiating recall with
each word are plotted as a function of presentation position. \textbf{Middle
panels.} The conditional probabilities of recalling each word are plotted as a
function of the relative position (lag) to the word recalled just-prior.
\textbf{Right panels.} The overall probabilities of recalling each word are
plotted as a function of presentation position. \textbf{All panels.} Error
ribbons denote bootstrap-estimated 95\% confidence intervals (calculated across
participants). Top panels display the recall dynamics for early lists in each
condition, and bottom panels display the recall dynamics for late lists.}

@@

    \caption{\textbf{Recall dynamics in feature-rich free recall (adaptive condition).} \textbf{Left panel.} The probabilities of
    initiating recall with each word are plotted as a function of presentation
    position. \textbf{Middle panel.} The conditional probabilities of recalling
    each word are plotted as a function of the relative position (lag) to the word
    recalled just-prior. \textbf{Right panel.} The overall probabilities of
    recalling each word are plotted as a function of presentation position.
    \textbf{All panels.} Error ribbons denote bootstrap-estimated 95\% confidence
    intervals (calculated across participants). Word-sorting policy (batch) is denoted by color.}

@@

    \caption{\textbf{Correlations between feature clustering scores (order manipulation conditions).}  Each column reflects one experimental condition.  The matrices in the top and middle
    rows display across-participant correlations between clustering scores for each feature dimension (top: order manipulation lists; middle: randomly ordered lists).  The matrices
    in the bottom row display the differences between the top and middle rows.}
        \label{fig:clustering-correlations}
\end{figure}

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{geometry}
\usepackage{natbib}
\usepackage{pxfonts}
\usepackage{graphicx}
\usepackage{newfloat}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{placeins}
\usepackage{rotating}
\usepackage{booktabs}

@@

\setcounter{equation}{0}
\setcounter{figure}{0}
\setcounter{table}{0}
\setcounter{page}{1} 
\setcounter{section}{0}
\makeatletter
\renewcommand{\theequation}{S\arabic{equation}}
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thetable}{S\arabic{table}}
\renewcommand{\bibnumfmt}[1]{[S#1]}
\renewcommand{\citenumfont}[1]{S#1}

\maketitle
\thispagestyle{empty}

\begin{table}[p]
    \centering
    \input{tables/abbreviations.tex}

    \caption{\textbf{List of abbreviations.} Used in tables in the main text.}

    \label{tab:abbreviations}
\end{table}

@@

\caption{\textbf{Recall dynamics in feature-rich free recall (random
conditions).} \textbf{Left panels.} The probabilities of initiating recall with
each word are plotted as a function of presentation position. \textbf{Middle
panels.} The conditional probabilities of recalling each word are plotted as a
function of the relative position (Lag) to the word recalled just-prior.
\textbf{Right panels.} The overall probabilities of recalling each word are
plotted as a function of presentation position. \textbf{All panels.} Error
ribbons denote bootstrap-estimated 95\% confidence intervals (calculated across
participants). Top panels display the recall dynamics for early lists in each
condition, and bottom panels display the recall dynamics for late lists.}

@@

    \caption{\textbf{Recall dynamics in feature-rich free recall (adaptive
    condition).} \textbf{Left panel.} The probabilities of initiating recall
    with each word are plotted as a function of presentation position.
    \textbf{Middle panel.} The conditional probabilities of recalling each word
    are plotted as a function of the relative position (Lag) to the word
    recalled just-prior. \textbf{Right panel.} The overall probabilities of
    recalling each word are plotted as a function of presentation position.
    \textbf{All panels.} Error ribbons denote bootstrap-estimated 95\%
    confidence intervals (calculated across participants). Word-sorting policy
    (batch) is denoted by color.}

@@

    \caption{\textbf{Correlations between feature clustering scores (order
    manipulation conditions).} Each column reflects one experimental condition.
    The matrices in the top and middle rows display across-participant
    correlations between clustering scores for each feature dimension (top:
    early lists; middle: late lists). The matrices in the bottom row display
    the differences between the top and middle rows.}

        \label{fig:clustering-correlations}
\end{figure}
